---
title: "Test presentation"
author: Tuyen Huynh
date: "24/10/2023"
output: beamer_presentation
theme: "Hannover"
---

```{r include=FALSE}
source("../time_series_modelling/data_weekly.R")
theme_set(theme_bw())
```

# Data description

## Epidemiological data

-   **Source**: Ho Chi Minh City CDC
-   **Temporal coverage**: 2000 -- 2022 (inclusive)
    -   **Train set**: 2000 -- 2017
    -   **Validation set**: 2018
    -   **Test set**: 2019
-   **Format**: Weekly aggregated admission
    -   Raw format is line listing -- each case admission is one row
-   **Spatial coverage**: Ho Chi Minh City
-   In-patient cases only
    -   out-patient data is only available from 2017

------------------------------------------------------------------------

```{r, incidence time series, fig.height=7, fig.width=12, echo=FALSE, fig.cap="Dengue weekly incidence time series"}
ggplot(incidence_weekly_df, aes(x = date_admitted, y = n)) +
  geom_line() +
  scale_x_yearweek(
    "Date",
    breaks = yearweek(paste0(seq(2000, 2023, 1), " W01")), minor_breaks = NULL,
    labels = as.character(seq(2000, 2023, 1))
  ) +
  scale_y_continuous("Case admitted")
```

------------------------------------------------------------------------

```{r, incidence splits, fig.height=7, fig.width=12, echo=FALSE, fig.cap="Train - validation - test set splits"}
incidence_weekly_df %>%
  filter_index("2000 W01" ~ "2019 W52") %>%
  ggplot(aes(x = date_admitted, y = n)) +
  geom_line() +
  geom_vline(xintercept = as.Date(yearweek("2018 W01")), color = "red") +
  geom_vline(xintercept = as.Date(yearweek("2019 W01")), color = "red") +
  scale_x_yearweek(
    "Date",
    breaks = yearweek(paste0(seq(2000, 2020, 1), " W01")), minor_breaks = NULL,
    labels = as.character(seq(2000, 2020, 1))
  ) +
  scale_y_continuous("Case admitted")
```

## Meteorological data

-   **Source**: ERA5 -- ECMWF atmospheric reanalysis (5th gen)
    -   **Variables**: 2m temperature, total precipitation, relative humidity
    -   All variables are daily aggregated
-   **Temporal coverage**: 1999 -- 2022 (inclusive)
    -   **Train set**: 2000 -- 2017
    -   **Validation set**: 2018
    -   **Test set**: 2019
-   Temporal resolution: Daily
-   Spatial coverage: Ho Chi Minh City\*

*\* cropped by Ho Chi Minh City 10km buffer bounding box and then spatially aggregated in R*

---

```{r message=FALSE, fig.cap='Weekly average 2m temperature', fig.width=12, fig.height=7, warning=FALSE, include=FALSE}
hcmc_temp_df %>%
  ggplot(aes(x = date, y = t2m)) +
  geom_line() +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs")) +
  scale_x_yearweek(
    "Date",
    breaks = yearweek(paste0(seq(1999, 2023, 1), " W01")), minor_breaks = NULL,
    labels = as.character(seq(1999, 2023, 1))
  ) +
  scale_y_continuous("Degree Celsius", breaks = seq(22, 32, 2))
```

---

```{r fig.height=7, fig.width=12, echo=FALSE, fig.cap="Weekly total precipitation"}
hcmc_precip_df %>%
  ggplot(aes(x = date, y = precip)) +
  geom_line() +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs")) +
  scale_x_yearweek(
    "Week",
    breaks = yearweek(paste0(seq(1999, 2023, 1), " W01")), minor_breaks = NULL,
    labels = as.character(seq(1999, 2023, 1))
  ) +
  scale_y_continuous("Millimeters")
```

---

```{r fig.height=7, fig.width=12, echo=FALSE, fig.cap="Weekly average relative humidity"}
hcmc_rh_df %>%
  ggplot(aes(x = date, y = rh)) +
  geom_line() +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs")) +
  scale_x_yearweek(
    "Week",
    breaks = yearweek(paste0(seq(1999, 2023, 1), " W01")), minor_breaks = NULL,
    labels = as.character(seq(1999, 2023, 1))
  ) +
  scale_y_continuous("Percent")
```


## Getting up

-   Turn off alarm
-   Get out of bed

## Breakfast

-   Eat eggs
-   Drink coffee

# In the evening

## Dinner

-   Eat spaghetti
-   Drink wine

------------------------------------------------------------------------

```{r, cars, fig.cap="A scatterplot.", echo=FALSE}
plot(cars)
```

## Going to sleep

-   Get in bed
-   Count sheep
