# Library

```{r}
library(sf)
library(stars)
library(tscount)
library(distributional)
library(parallel)
library(pbapply)

source("../utils/data_weekly.R", chdir = TRUE)
source("../utils/covar_fns.R", chdir = TRUE)
source("../utils/regression_recur_miso.R", chdir = TRUE)
source("../utils/performance_checking_framework.R", chdir = TRUE)
```

# Weather data

## Temperature data

```{r}
plot_covar(hcmc_temp_df, "Temperature (°C)", "Weekly mean 2m temperature - ERA5 reanalysis")

ggsave("./svgs/weekly_t2m_ts.svg", width = 10, height = 7)

hist(hcmc_temp_df$t2m)
```

## Precipitation data

```{r}
plot_covar(hcmc_precip_df, "Precipitation (mm)", "Weekly total precipitation ERA5 - reanalysis")

ggsave("./svgs/weekly_precip_ts.svg", width = 10, height = 7)

hist(hcmc_precip_df$precip)
```

## Humidity data

```{r}
plot_covar(hcmc_rh_df, "Relative Humidity (%)", "Weekly mean relative humidity - ERA5 reanalysis")

ggsave("./svgs/weekly_rh_ts.svg", width = 10, height = 7)

hist(hcmc_rh_df$rh)
```


```{r}
incidence_weekly_weather_df
```

## Specific humidity
```{r}
plot_covar(hcmc_sh_df, "Specific Humidity (g/kg)", "Weekly mean specific humidity - ERA5 reanalysis")

ggsave("./svgs/weekly_sh_ts.svg", width = 10, height = 7)

hist(hcmc_sh_df$sh)
```

## Wind speed
```{r}
plot_covar(
  hcmc_ws_df,
  "Wind speed intensity at 10 meters (m/s)",
  "Weekly mean wind speed intensity - ERA5 reanalysis"
)

ggsave("./svgs/weekly_ws_ts.svg", width = 10, height = 7)

hist(hcmc_ws_df$ws)
```

## Hydrological balance

Daily hydrological balance (`evaporation - precipitation`) If `hb`>0, the area is accumulates water. If `hb` <0, the area loses water (in m)

```{r}
plot_covar(
  hcmc_hb_df,
  "Hydrological balance",
  "Weekly total hydrological balance - ERA5 reanalysis",
  layer(
    geom = "hline", stat = "identity", position = "identity",
    params = list(yintercept = 0, color = "red", linetype = "dashed")
  )
)

ggsave("./svgs/weekly_hb_ts.svg", width = 10, height = 7)

hist(hcmc_hb_df$hb)
```

## Solar radiation
Accumulated solar radiation downwards. This parameter is the amount of solar radiation (also known as shortwave radiation) that reaches a horizontal plane at the surface of the Earth. It is important to highlight that this parameter comprises both direct and diffuse solar radiation. (J/m2)

```{r}
plot_covar(
  hcmc_ssdr_df,
  "Accumulated solar radiation downwards (J/m²)",
  "Weekly total accumulated solar radiation downwards - ERA5 reanalysis"
)

ggsave("./svgs/weekly_ssdr_ts.svg", width = 10, height = 7)

hist(hcmc_ssdr_df$ssdr)
```

## Max and min temperature

```{r}
plot_covar(
  hcmc_mx_mn2t24_df %>% pivot_longer(-date) %>% relocate(value, .after = date),
  "Temperature (°C)",
  "Weekly mean maximum and minimum temperature - ERA5 reanalysis",
  list(),
  color = name
)

ggsave("./svgs/weekly_mx_mn2t24_ts.svg", width = 10, height = 7)

hist(hcmc_mx_mn2t24_df$mn2t24)
hist(hcmc_mx_mn2t24_df$mx2t24)
```

## Max and min relative humidity

```{r}
plot_covar(
  hcmc_mx_mnrh24_df %>% pivot_longer(-date) %>% relocate(value, .after = date),
  "Relative humidity",
  "Weekly mean maximum and minimum relative humidity - ERA5 reanalysis",
  list(),
  color = name
)

ggsave("./svgs/weekly_mx_mnrh24_ts.svg", width = 10, height = 7)

hist(hcmc_mx_mnrh24_df$mnrh24)
hist(hcmc_mx_mnrh24_df$mxrh24)
```

## Max and min specific humidity

```{r}
plot_covar(
  hcmc_mx_mnsh24_df %>% pivot_longer(-date) %>% relocate(value, .after = date),
  "Specific humidity",
  "Weekly mean maximum and minimum specific humidity - ERA5 reanalysis",
  scale_alpha_continuous(guide = "none"),
  color = name, alpha = 0.9
)

ggsave("./svgs/weekly_mx_mnsh24_ts.svg", width = 10, height = 7)

hist(hcmc_mx_mnsh24_df$mnsh24)
hist(hcmc_mx_mnsh24_df$mxsh24)
```


# Covariable selection

```{r}
covar_poi_perf <- function(covar_name) {
  forecast_df <- recur_miso(
    train_weekly_weather_df, test_weekly_weather_df,
    seq(1, 49, 3),
    model = list(past_obs = 1), xreg_names = c(covar_name),
    link = "log", distr = "poisson"
  ) %>%
    mutate(date = yearweek(paste0("2019 W", actualweek)), .before = everything())

  pre_perf_df <- forecast_df %>%
    select(date, dist, preds, startweek) %>%
    left_join(test_weekly_df, by = c("date" = "date_admitted")) %>%
    rename(.mean = preds)

  chunks_forecast_res_df <- chunks_forecast_perf(
    pre_perf_df, sprintf("Poisson w/ %s", covar_name),
    scoringRules::crps_sample, matrix(parameters(dist)$x[[1]], nrow = n()),
    log_model_perf = FALSE
  )

  chunks_forecast_res_df %>%
    summarise(across(c("RMSE", "CRPS"), mean)) %>%
    mutate(model = sprintf("Poisson w/ %s", covar_name), .before = everything())
}

covar_names <- incidence_weekly_weather_df %>%
  as_tibble() %>%
  select(-c(date_admitted, n)) %>%
  colnames()
covar_names
```

```{r}
cl <- makeCluster(7)
invisible(clusterEvalQ(cl, library(tidyverse)))
invisible(clusterEvalQ(cl, library(magrittr)))
invisible(clusterEvalQ(cl, library(tscount)))
invisible(clusterEvalQ(cl, library(tsibble)))
invisible(clusterEvalQ(cl, library(distributional)))
clusterExport(
  cl,
  c("recur_miso", "train_weekly_weather_df", "test_weekly_weather_df", "test_weekly_df", "chunks_forecast_perf")
)

poi_covar_perfs <- pblapply(covar_names, covar_poi_perf, cl = cl) %>% list_c()

stopCluster(cl)
```

```{r}
poi_covar_perfs
```


```{r}
poi_covar_perfs %>%
  ggplot(aes(x = CRPS, y = fct_reorder(model, desc(CRPS)))) +
  geom_col() +
  scale_y_discrete("Model")
```
