---
title: "Dengue weekly incidence modelling"
output: 
  html_document:
    df_print: paged
    toc: yes
    theme: journal
---

**Knitted at: `r Sys.time()`**

# Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)

library(feasts)
library(fable.prophet)
library(fabletools)
library(fable)

library(tsibble)
library(lubridate)

library(parallel)
```

# Settings
```{r}
theme_set(theme_bw())
```


# Data ingestion

```{r}
source("../data_weekly.R", chdir = TRUE)
```


## Incidence data

```{r}
ggplot(incidence_weekly_df, aes(x = date_admitted, y = n)) +
  geom_step() +
  scale_x_yearweek(
    "Date",
    breaks = yearweek(paste0(seq(2000, 2023, 1), " W01")), minor_breaks = NULL,
    labels = as.character(seq(2000, 2023, 1))
  ) +
  scale_y_continuous("Case admitted") +
  ggtitle("Dengue weekly incidence")

ggsave("./svgs/weekly_incidence_ts.svg", width = 12, height = 7)
```

```{r}
train_weekly_df <- train_weekly_df %>% bind_rows(val_weekly_df)
train_weekly_df %>% tail()

train_weekly_weather_df <- train_weekly_weather_df %>% bind_rows(val_weekly_weather_df)
train_weekly_weather_df %>% tail()
```

### Train test split
```{r}
incidence_weekly_df %>%
  filter_index("2000 W01" ~ "2019 W52") %>%
  ggplot(aes(x = date_admitted, y = n)) +
  geom_step() +
  geom_vline(xintercept = as.Date(yearweek("2019 W01")), color = "red") +
  scale_x_yearweek(
    "Date",
    breaks = yearweek(paste0(seq(2000, 2020, 1), " W01")), minor_breaks = NULL,
    labels = as.character(seq(2000, 2020, 1))
  ) +
  scale_y_continuous("Case admitted") +
  ggtitle("Dengue weekly incidence")

ggsave("./svgs/weekly_incidence_split_ts.svg", width = 12, height = 7)
```


# Time series analysis

## STL Decomposition

```{r}
incidence_weekly_df %>%
  model(
    stl_decomp = STL(n ~ season(period = 52, window = "periodic"), robust = TRUE)
  ) %>%
  components() %>%
  autoplot() + xlab("Date")

# ggsave("./svgs/decomp_stl_additive.svg", width = 10, height = 7)
```


## Homoscedasticity

```{r}
skedastic::white(lm(n ~ date_admitted, data = train_weekly_df))
```

```{r}
boxcox_mle <- unclass(MASS::boxcox(lm(n ~ date_admitted, data = train_weekly_df))) %>% as_tibble()

boxcox_white_df <- map(boxcox_mle$x, \(lambda) {
  tibble(
    lambda = lambda,
    transformed_x = list(box_cox(train_weekly_df$n, lambda)),
    white_pvalue = skedastic::white(
      lm(unlist(transformed_x) ~ train_weekly_df$date_admitted)
    )$p.value
  )
}) %>%
  list_c()

boxcox_white_df %>%
  left_join(boxcox_mle, by = c("lambda" = "x")) %>%
  ggplot(aes(x = lambda)) +
  geom_line(aes(y = white_pvalue), color = "red") +
  geom_line(aes(y = (y - min(y)) / 1000000), color = "blue") +
  scale_y_continuous(
    "White test p-value",
    sec.axis = sec_axis(trans = ~ . * 1000000 + min(boxcox_mle$y), name = "log-Likelihood")
  )
```

```{r}
white_lambda <- boxcox_white_df %>%
  filter(lambda > -1) %>%
  filter(white_pvalue == max(white_pvalue)) %>%
  pull(lambda)
boxcox_lambda <- boxcox_mle %>%
  filter(y == max(y)) %>%
  pull(x)
guerrero_lambda <- train_weekly_df %>%
  features(n, features = guerrero) %>%
  pull(lambda_guerrero)

white_lambda
boxcox_lambda
guerrero_lambda
```

## Log transformation

```{r}
incidence_weekly_df %<>% mutate(n = log(n))
train_weekly_df %<>% mutate(n = log(n))
test_weekly_df %<>% mutate(n = log(n))

ggplot(incidence_weekly_df, aes(x = date_admitted, y = n)) +
  geom_line() +
  xlab("Date") +
  ylab("Log-transformed incidence")

ggsave("./svgs/weekly_incidence_log_trans.svg", width = 10, height = 7)
```


```{r}
train_weekly_weather_df %<>% mutate(n = log(n))
test_weekly_weather_df %<>% mutate(n = log(n))
```

# Modelling

## Misc

### Performance checking 

```{r}
model_perfs <- tibble(
  model = character(),
  RMSE = numeric(),
  MAE = numeric()
)

forecast_perf <- function(forecast, actual, model_name) {
  rmse <- sqrt(mean((actual - forecast)^2))
  mae <- mean(abs(actual - forecast))

  print(sprintf("Test RMSE: %f", rmse))
  print(sprintf("Test MAE: %f", mae))

  model_perfs <<- model_perfs %>%
    bind_rows(tibble(model = model_name, RMSE = rmse, MAE = mae))
}
```

### Forecast framework
```{r}
forecast_layer <- function(frcst_df, funnel = TRUE) {
  frcst_df %<>%
    group_by(startweek)

  if (funnel) {
    frcst_df %<>%
      group_map(\(.x, .y){
        target_date <- min(.x$date_admitted) - 1
        target_row <- incidence_weekly_df %>%
          filter(date_admitted == target_date) %>%
          mutate(
            n = exp(n),
            .mean = n, uppers = n, lowers = n,
            startweek = .y$startweek
          )

        .x %>%
          mutate(startweek = .y$startweek) %>%
          add_row(
            target_row,
            .before = 0
          )
      }) %>%
      list_c() %>%
      group_by(startweek)
  }

  lapply(
    frcst_df %>% group_split(),
    \(df)
    c(layer(
      data = df,
      geom = "ribbon", stat = "identity", position = "identity",
      mapping = aes(x = date_admitted, ymin = lowers, ymax = uppers),
      params = list(alpha = 0.5, fill = "pink")
    ), layer(
      data = df,
      geom = "line", stat = "identity", position = "identity",
      mapping = aes(x = date_admitted, y = .mean), params = list(color = "red")
    ))
  )
}

forecast_plot_default <- function(fit_df, actual_df, plot_title) {
  ggplot(actual_df) +
    geom_line(aes(x = date_admitted, y = n)) +
    forecast_layer(fit_df) +
    scale_x_yearweek(
      "Week",
      breaks = test_weekly_df$date_admitted[seq(0, 52, 3) + 1],
      labels = as.character(test_weekly_df$date_admitted[seq(0, 52, 3) + 1]) %>% str_extract("W\\d+"),
      minor_breaks = NULL
    ) +
    scale_y_continuous("Incidence") +
    ggtitle(plot_title)
}

forecast_chunks <- function(
    train_set, test_set,
    start_indices,
    model_fn, formula, ...,
    horizon = 4, cl = NULL) {
  if (!missing(cl)) {
    clusterEvalQ(cl, suppressPackageStartupMessages(library(dplyr)))
    clusterEvalQ(cl, library(fabletools))
    clusterExport(cl, c("train_set", "test_set"), environment())
  }
  model_fn <- match.fun(model_fn)

  pbapply::pblapply(start_indices, \(start_idx){
    train_df <- train_set %>%
      bind_rows(test_set %>% slice_head(n = start_idx)) %>%
      tail(nrow(train_set))


    fit <- train_df %>% model(model = model_fn(!!enquo(formula), ...))

    new_data <- test_set %>%
      slice_tail(n = 52 - start_idx) %>%
      head(horizon)

    fit %>%
      forecast(new_data = new_data) %>%
      as_tibble() %>%
      mutate(
        .model = format(fit$model),
        startweek = start_idx,
        uppers = hilo(n)$upper,
        lowers = hilo(n)$lower
      )
  }, cl = cl) %>%
    list_c()
}
```

### Differencing

Quickly check if any differencing needed, both seasonal and non-seasonal

```{r}
train_weekly_df %>% features(n, unitroot_ndiffs)
train_weekly_df %>% features(n, unitroot_nsdiffs)
```

```{r}
train_weekly_df %>%
  gg_tsdisplay(
    difference(n),
    plot_type = "partial",
    lag = 52
  )

train_weekly_df %>%
  gg_tsdisplay(
    difference(n, 52),
    plot_type = "partial",
    lag = 208
  )
```


## AR

### Base model
```{r}
ar_fit <- train_weekly_df %>% model(AR(n))
report(ar_fit)

cat("\n\n")

coefs <- ar_fit %>% coef() %>% slice(-1) %>% select(c(term, estimate)) %>% deframe() %>% as.list()
coefs
```

### Chunks
```{r}
ar_chunks_fit <- forecast_chunks(
  train_weekly_df, test_weekly_df, seq(0, 49, 3),
  AR, n ~ order(p = 10, fixed = coefs)
)

forecast_plot_default(
  ar_chunks_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - AR(10)"
)

ggsave("./svgs/forecast_ar10.svg", width = 10, height = 7)
```

```{r}
pre_perf <- ar_chunks_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(pre_perf$.mean),
  exp(pre_perf$n), "AR(10)"
)
```

## MA

### Base model

```{r}
lapply(0:7, \(q){
  fit <- train_weekly_df %>%  model(ARIMA(n ~ pdq(0, 0, q) + PDQ(0, 0, 0)))
  tibble(q = q, aicc = (glance(fit))$AICc)
}) %>% list_c()
```


```{r}
ma_fit <- train_weekly_df %>%  model(ARIMA(n ~ pdq(0, 0, 6) + PDQ(0, 0, 0)))
report(ma_fit)

cat("\n\n")

coefs <- ma_fit %>% coef() %>% slice(1:6) %>% select(c(term, estimate)) %>% deframe() %>% as.list()
coefs
```

### Chunks

```{r}
ma_chunks_fit <- forecast_chunks(
  train_weekly_df, test_weekly_df, seq(0, 49, 3),
  ARIMA, n ~ pdq(0, 0, 6, fixed = coefs) + PDQ(0, 0, 0)
)

forecast_plot_default(
  ma_chunks_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - MA(6)"
)

ggsave("./svgs/forecast_ma6.svg", width = 10, height = 7)
```


```{r}
pre_perf <- ma_chunks_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(pre_perf$.mean),
  exp(pre_perf$n), "MA(6)"
)
```


## ARIMA
### Base model
```{r}
arima_fit <- train_weekly_df %>% model(ARIMA(n ~ PDQ(0, 0, 0), stepwise = FALSE))
report(arima_fit)

coefs <- arima_fit %>% coef() %>% select(c(term, estimate)) %>% deframe() %>% as.list()
coefs
```

### Chunks
```{r}
arima_chunks_fit <- forecast_chunks(
  train_weekly_df, test_weekly_df, seq(0, 49, 3),
  ARIMA, n ~ pdq(3,1,3, fixed = coefs) + PDQ(0, 0, 0)
)

forecast_plot_default(
  arima_chunks_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - ARIMA(3,1,3)"
)

ggsave("./svgs/forecast_arima.svg", width = 10, height = 7)
```


```{r}
pre_perf <- arima_chunks_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(pre_perf$.mean),
  exp(pre_perf$n), "ARIMA(3,1,3)"
)
```

## ARIMAX
### Base model
```{r}
arimax_t2m_fit <- train_weekly_weather_df %>% 
  model(ARIMA(n ~ xreg(t2m) + PDQ(0, 0, 0), stepwise = FALSE))
report(arimax_t2m_fit)

t2m_coefs <- arimax_t2m_fit %>% coef() %>% select(c(term, estimate)) %>% deframe() %>% as.list()
t2m_coefs

arimax_precip_fit <- train_weekly_weather_df %>% 
  model(ARIMA(n ~ xreg(precip) + PDQ(0, 0, 0), stepwise = FALSE))
report(arimax_precip_fit)

precip_coefs <- arimax_precip_fit %>% coef() %>% select(c(term, estimate)) %>% deframe() %>% as.list()
precip_coefs

arimax_rh_fit <- train_weekly_weather_df %>% 
  model(ARIMA(n ~ xreg(rh) + PDQ(0, 0, 0), stepwise = FALSE))
report(arimax_rh_fit)

rh_coefs <- arimax_rh_fit %>% coef() %>% select(c(term, estimate)) %>% deframe() %>% as.list()
rh_coefs
```

### Chunks

```{r}
arimax_t2m_chunks_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  ARIMA, n ~ xreg(t2m, fixed = t2m_coefs[7]) + pdq(3, 1, 3, fixed = t2m_coefs[-7]) + PDQ(0, 0, 0)
)
arimax_t2m_chunks_fit

arimax_precip_chunks_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  ARIMA, n ~ xreg(precip, fixed = precip_coefs[7]) + pdq(3, 1, 3, fixed = precip_coefs[-7]) + PDQ(0, 0, 0)
)
arimax_precip_chunks_fit

arimax_rh_chunks_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  ARIMA, n ~ xreg(rh, fixed = rh_coefs[7]) + pdq(3, 1, 3, fixed = rh_coefs[-7]) + PDQ(0, 0, 0)
)
arimax_rh_chunks_fit
```

```{r}
forecast_plot_default(
  arimax_t2m_chunks_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - ARIMA(3,1,3) + mean 2m temperature"
)
ggsave("./svgs/forecast_arimax_t2m.svg", width = 10, height = 7)

forecast_plot_default(
  arimax_precip_chunks_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - ARIMA(3,1,3) + total precipitation"
)
ggsave("./svgs/forecast_arimax_precip.svg", width = 10, height = 7)

forecast_plot_default(
  arimax_rh_chunks_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - ARIMA(3,1,3) + mean relative humidity"
)
ggsave("./svgs/forecast_arimax_rh.svg", width = 10, height = 7)
```


```{r}
t2m_pre_perf <- arimax_t2m_chunks_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(t2m_pre_perf$.mean),
  exp(pre_perf$n), "ARIMA(3,1,3) + t2m"
)

precip_pre_perf <- arimax_precip_chunks_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(precip_pre_perf$.mean),
  exp(pre_perf$n), "ARIMA(3,1,3) + precip"
)

rh_pre_perf <- arimax_rh_chunks_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(rh_pre_perf$.mean),
  exp(pre_perf$n), "ARIMA(3,1,3) + rh"
)
```

### Combining covars

```{r}
get_coefs <- \(fit) fit %>% coef() %>%select(c(term, estimate)) %>% deframe() %>% as.list()

arimax_t2m_precip_fit <- train_weekly_weather_df %>% 
  model(ARIMA(n ~ xreg(t2m, precip) + PDQ(0, 0, 0), stepwise = FALSE))
arimax_t2m_rh_fit <- train_weekly_weather_df %>% 
  model(ARIMA(n ~ xreg(t2m, rh) + PDQ(0, 0, 0), stepwise = FALSE))
arimax_precip_rh_fit <- train_weekly_weather_df %>% 
  model(ARIMA(n ~ xreg(precip, rh) + PDQ(0, 0, 0), stepwise = FALSE))
arimax_weather_fit <- train_weekly_weather_df %>% 
  model(ARIMA(n ~ xreg(t2m, precip, rh) + PDQ(0, 0, 0), stepwise = FALSE))

t2m_precip_coefs <- get_coefs(arimax_t2m_precip_fit)
t2m_precip_coefs
t2m_rh_coefs <- get_coefs(arimax_t2m_rh_fit)
t2m_rh_coefs
precip_rh_coefs <- get_coefs(arimax_precip_rh_fit)
precip_rh_coefs
weather_coefs <- get_coefs(arimax_weather_fit)
weather_coefs
```


```{r}
arimax_t2m_precip_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  ARIMA, 
  n ~ xreg(t2m, precip, fixed = t2m_precip_coefs[c(7,8)]) + pdq(3,1,3,fixed = t2m_precip_coefs[-c(7,8)]) + PDQ(0, 0, 0)
)
arimax_t2m_precip_fit

arimax_t2m_rh_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  ARIMA, n ~ xreg(t2m, rh, fixed = t2m_rh_coefs[c(7,8)]) + pdq(3,1,3,fixed = t2m_rh_coefs[-c(7,8)]) + PDQ(0, 0, 0)
)
arimax_t2m_rh_fit

arimax_precip_rh_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  ARIMA, n ~ xreg(precip, rh, fixed = precip_rh_coefs[c(7,8)]) + pdq(3,1,3,fixed = precip_rh_coefs[-c(7,8)]) + PDQ(0, 0, 0)
)
arimax_precip_rh_fit

arimax_weather_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  ARIMA, n ~ xreg(t2m, precip, rh, fixed = weather_coefs[c(7,8,9)]) + pdq(3,1,3,fixed = weather_coefs[-c(7,8,9)]) + PDQ(0, 0, 0),
  stepwise = FALSE
)
arimax_weather_fit
```

```{r}
forecast_plot_default(
  arimax_t2m_precip_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - ARIMA(3,1,3) + t2m + tp"
)
ggsave("./svgs/forecast_arimax_t2m_precip.svg", width = 10, height = 7)

forecast_plot_default(
  arimax_t2m_rh_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - ARIMA(3,1,3) + t2m + rh"
)
ggsave("./svgs/forecast_arimax_t2m_rh.svg", width = 10, height = 7)

forecast_plot_default(
  arimax_precip_rh_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - ARIMA(3,1,3) + tp + rh"
)
ggsave("./svgs/forecast_arimax_precip_rh.svg", width = 10, height = 7)

forecast_plot_default(
  arimax_weather_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - ARIMA(3,1,3) + t2m + tp + rh"
)
ggsave("./svgs/forecast_arimax_weather.svg", width = 10, height = 7)
```

```{r}
t2m_precip_pre_perf <- arimax_t2m_precip_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(t2m_precip_pre_perf$.mean),
  exp(pre_perf$n), "ARIMA(3,1,3) + t2m + tp"
)

t2m_rh_pre_perf <- arimax_t2m_rh_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(t2m_rh_pre_perf$.mean),
  exp(pre_perf$n), "ARIMA(3,1,3) + t2m + rh"
)

precip_rh_pre_perf <- arimax_precip_rh_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(precip_rh_pre_perf$.mean),
  exp(pre_perf$n), "ARIMA(3,1,3) + tp + rh"
)

weather_pre_perf <- arimax_weather_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(weather_pre_perf$.mean),
  exp(pre_perf$n), "ARIMA(3,1,3) + t2m + tp + rh"
)
```

## SARIMA
### Base model
```{r}
# 11mins
system.time(
  {sarima_fit <- train_weekly_df %>% model(ARIMA(n))}
)
report(sarima_fit)

sarima_coefs <- sarima_fit %>% coef() %>% head(-1) %>% select(c(term, estimate)) %>% deframe() %>% as.list()
sarima_coefs
```



### Chunks
```{r}
cl <- makeCluster(6)
sarima_chunks_fit <- forecast_chunks(
  train_weekly_df, test_weekly_df, seq(0, 49, 3),
  ARIMA, n ~ pdq(1,0,1, fixed = sarima_coefs[-3]) + PDQ(1, 1, 0, fixed = sarima_coefs[3]),
  cl = cl
)
stopCluster(cl)


forecast_plot_default(
  sarima_chunks_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - SARIMA"
)

ggsave("./svgs/forecast_sarima.svg", width = 10, height = 7)
```


```{r}
pre_perf <- sarima_chunks_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(pre_perf$.mean),
  exp(pre_perf$n), "SARIMA"
)
```

## SARIMAX

SARIMAX - Seasonal Auto-Regressive Integrated Moving Average with eXogenous factors

```{r}
# cl <- makeCluster(8)
#
# arimax_t2m_fit <- forecast_chunks(
#   train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
#   ARIMA, n ~ xreg(t2m),
#   stepwise = FALSE, cl = cl
# )
# arimax_t2m_fit
#
# arimax_precip_fit <- forecast_chunks(
#   train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
#   ARIMA, n ~ xreg(precip),
#   stepwise = FALSE, cl = cl
# )
# arimax_precip_fit
#
# arimax_rh_fit <- forecast_chunks(
#   train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
#   ARIMA, n ~ xreg(rh),
#   stepwise = FALSE, cl = cl
# )
# arimax_rh_fit
#
# stopCluster(cl)
```

## Prophet weekly

```{r}
prophet_addi_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  prophet, n ~ season(period = 52, order = 10, type = "additive")
)
prophet_multi_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  prophet, n ~ season(period = 52, order = 10, type = "multiplicative")
)
```


```{r}
forecast_plot_default(
  prophet_addi_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - Prophet additive"
)

ggsave("./svgs/forecast_prophet_addi.svg", width = 10, height = 7)

forecast_plot_default(
  prophet_multi_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - Prophet multiplicative"
)

ggsave("./svgs/forecast_prophet_multi.svg", width = 10, height = 7)
```

```{r}
addi_pre_perf <- prophet_addi_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(addi_pre_perf$.mean),
  exp(pre_perf$n), "Prophet additive"
)

multi_pre_perf <- prophet_multi_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(multi_pre_perf$.mean),
  exp(pre_perf$n), "Prophet multiplicative"
)
```

### With exogenous regressors


```{r}
prophet_t2m_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  prophet, n ~ xreg(t2m) + season(period = 52, order = 10, type = "additive")
)
prophet_precip_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  prophet, n ~ xreg(precip) + season(period = 52, order = 10, type = "additive")
)
prophet_rh_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  prophet, n ~ xreg(rh) + season(period = 52, order = 10, type = "additive")
)
```

```{r}
forecast_plot_default(
  prophet_t2m_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - Prophet additive + mean 2m temperature"
)

ggsave("./svgs/forecast_prophet_t2m.svg", width = 10, height = 7)

forecast_plot_default(
  prophet_precip_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - Prophet additive + total precipitation"
)

ggsave("./svgs/forecast_prophet_precip.svg", width = 10, height = 7)

forecast_plot_default(
  prophet_rh_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - Prophet additive + mean relative humidity"
)

ggsave("./svgs/forecast_prophet_rh.svg", width = 10, height = 7)
```

```{r}
prophet_t2m_pre_perf <- prophet_t2m_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(prophet_t2m_pre_perf$.mean),
  exp(pre_perf$n), "Prophet additive + mean 2m temperature"
)

prophet_precip_pre_perf <- prophet_precip_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(prophet_precip_pre_perf$.mean),
  exp(pre_perf$n), "Prophet additive + total precipitation"
)

prophet_rh_pre_perf <- prophet_rh_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(prophet_rh_pre_perf$.mean),
  exp(pre_perf$n), "Prophet additive + mean relative humidity"
)
```


### With holidays

```{r fig.height=15, fig.width=15, warning=FALSE}
pub_holidays <- map(2000:2022, \(year){
  c(
    sprintf("%d-01-01", year),
    sprintf("%d-12-29", subtract(year, 1)) %>% lunR::lunar_to_gregorian(),
    sprintf("%d-03-10", year) %>% lunR::lunar_to_gregorian(),
    sprintf("%d-04-30", year),
    sprintf("%d-05-01", year),
    sprintf("%d-09-02", year)
  )
}) %>%
  list_c() %>%
  as.Date()

vn_pub_holidays <- tsibble(
  date = pub_holidays,
  holiday = rep(
    c("New Year", "Tet", "Hung King", "Reunification", "Labor Day", "Independence Day"),
    23
  ),
  lower_window = rep(c(0, 0, 0, 0, 0, 0), 23),
  upper_window = rep(c(1, 7, 1, 1, 1, 2), 23),
  index = date
)

vn_pub_holidays_train <- vn_pub_holidays %>% filter(year(date) < 2019)

incidence_weekly_df %>%
  mutate(year = year(date_admitted)) %>%
  autoplot() +
  geom_vline(data = vn_pub_holidays, aes(xintercept = date), color = "red", alpha = 0.3) +
  facet_wrap(~year, scales = "free_x")
```

```{r}
prophet_holiday_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  prophet, n ~ season(period = 52, order = 10, type = "additive") + holiday(vn_pub_holidays_train)
)
```

```{r}
forecast_plot_default(
  prophet_holiday_fit %>% mutate(across(c(.mean, uppers, lowers), exp)),
  test_weekly_df %>% mutate(n = exp(n)),
  "4 week forecast - Prophet additive + holidays"
)

ggsave("./svgs/forecast_prophet_holiday.svg", width = 10, height = 7)
```


```{r}
prophet_holiday_pre_perf <- prophet_holiday_fit %>%
  select(date_admitted, .mean) %>%
  left_join(test_weekly_df, by = "date_admitted")

forecast_perf(
  exp(prophet_holiday_pre_perf$.mean),
  exp(pre_perf$n), "Prophet additive + holiday"
)
```



# Comparison
```{r}
model_perfs
```

```{r}
model_perfs %>% write_csv("parametric_models_perf.csv")
```
