---
output: 
  html_document:
    df_print: paged
    toc: yes
    theme: journal
---

**Knitted at: `r Sys.time()`**

# Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)
library(tscount)
library(tsibble)
library(feasts)
library(patchwork)
library(fable)

library(pbapply)
library(parallel)
library(foreach)
library(doParallel)

library(distributional)
```

# Settings
```{r}
theme_set(theme_bw())
set.seed(123)
```


# Data ingestion

```{r}
source("../utils/data_weekly.R", chdir = TRUE)
```


## Incidence data

```{r}
# ggplot(incidence_weekly_df, aes(x = date_admitted, y = n)) +
#   geom_line() +
#   scale_x_yearweek(
#     "Date",
#     breaks = yearweek(paste0(seq(2000, 2023, 1), " W01")), minor_breaks = NULL,
#     labels = as.character(seq(2000, 2023, 1))
#   ) +
#   scale_y_continuous("Case admitted") +
#   ggtitle("Dengue weekly incidence")

# ggsave("weekly_incidence_ts.svg", width = 12, height = 7)
```

### Train test split
```{r}
# incidence_weekly_df %>%
#   filter_index("2000 W01" ~ "2019 W52") %>%
#   ggplot(aes(x = date_admitted, y = n)) +
#   geom_line() +
#   geom_vline(xintercept = as.Date(yearweek("2019 W01")), color = "red") +
#   scale_x_yearweek(
#     "Date",
#     breaks = yearweek(paste0(seq(2000, 2020, 1), " W01")), minor_breaks = NULL,
#     labels = as.character(seq(2000, 2020, 1))
#   ) +
#   scale_y_continuous("Case admitted") +
#   ggtitle("Dengue weekly incidence")

# ggsave("weekly_incidence_split_ts.svg", width = 12, height = 7)
```


```{r}
train_weekly_df <- train_weekly_df %>% bind_rows(val_weekly_df)
train_weekly_df %>% tail()

train_weekly_weather_df <- train_weekly_weather_df %>% bind_rows(val_weekly_weather_df)
train_weekly_weather_df %>% tail()
```


# Modelling

## Performance checking framework

```{r}
model_perfs <- tibble(
  model = character(),
  RMSE = numeric(),
  CRPS = numeric()
)

source("../utils/performance_checking_framework.R", chdir = TRUE)
```


```{r}
source("../utils/forecast_plotting.R", chdir = TRUE)
source("../utils/chunks_forecasting.R", chdir = TRUE)

forecast_plot_default <- function(fit_df, actual_df, plot_title, funnel = TRUE) {
  ggplot(actual_df) +
    geom_line(aes(x = date_admitted, y = n)) +
    forecast_layer(fit_df, funnel = funnel) +
    scale_x_yearweek(
      "Week",
      breaks = actual_df$date_admitted[seq(0, 52, 3) + 1],
      labels = as.character(actual_df$date_admitted[seq(0, 52, 3) + 1]) %>% str_extract("W\\d+"),
      minor_breaks = NULL
    ) +
    scale_y_continuous("Incidence") +
    ggtitle(plot_title)
}
```

## Model fitting and forecast framework


```{r}
source("../utils/regression_recur_miso.R", chdir = TRUE)
```

# Linear models
```{r}
covar_names <- train_weekly_weather_df %>%
  as_tibble() %>%
  select(-c(date_admitted, n)) %>%
  colnames()
covar_names
```


## Simple linear regression

```{r}
lr_fits <- lapply(covar_names, \(covar){
  fit <- forecast_chunks(
    train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
    TSLM, as.formula(sprintf("n ~ %s", covar))
  )

  pre_perf_df <- fit %>%
    select(date_admitted, n, .mean, startweek) %>%
    rename(dist = n) %>%
    left_join(test_weekly_df, by = "date_admitted")

  chunks_forecast_perf(
    pre_perf_df, sprintf("LR + %s", covar),
    scoringRules::crps_norm, mean(dist), sqrt(variance(dist))
  )

  fit
})
```

```{r}
names(lr_fits) <- covar_names
# lr_fits

model_perfs

forecast_plot_default(
  lr_fits$mxsh24, test_weekly_df, "Linear regression + maximum specific humidity", FALSE
)

incidence_weekly_weather_df %>%
  drop_na() %>%
  select(n, mxsh24) %>%
  mutate(n = log(n)) %>%
  pivot_longer(-date_admitted) %>%
  ggplot(aes(x = date_admitted, y = value, color = name)) +
  geom_line()
```


## Multiple linear regression

```{r}
mlr_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  TSLM, as.formula(sprintf("n ~ %s", paste(covar_names, collapse = " + ")))
)

pre_perf_df <- mlr_fit %>%
  select(date_admitted, n, .mean, startweek) %>%
  rename(dist = n) %>%
  left_join(test_weekly_df, by = "date_admitted")

chunks_forecast_perf(
  pre_perf_df, "MLR + all weather covar",
  scoringRules::crps_norm, mean(dist), sqrt(variance(dist))
)

forecast_plot_default(mlr_fit, test_weekly_df, "Multiple linear regression", FALSE)
```

### Covariable selection

```{r}
full_model <- lm(
  n ~ .,
  data = train_weekly_weather_df %>%
    as_tibble() %>%
    select(-date_admitted)
)

step_selected_full_model <- olsrr::ols_step_both_aic(full_model)

plot(step_selected_full_model)
```

```{r}
step_selected_mlr_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  TSLM, as.formula(step_selected_full_model$model)
)

pre_perf_df <- step_selected_mlr_fit %>%
  select(date_admitted, n, .mean, startweek) %>%
  rename(dist = n) %>%
  left_join(test_weekly_df, by = "date_admitted")

chunks_forecast_perf(
  pre_perf_df, "MLR + stepwise selected weather covar",
  scoringRules::crps_norm, mean(dist), sqrt(variance(dist))
)

forecast_plot_default(
  step_selected_mlr_fit, test_weekly_df,
  "Multiple linear regression + stepwise selected weather covar", FALSE
)
```

# Other predictors

## Trend

```{r}
trend_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  TSLM, as.formula(sprintf("n ~ %s + trend()", paste(covar_names, collapse = " + ")))
)

pre_perf_df <- trend_fit %>%
  select(date_admitted, n, .mean, startweek) %>%
  rename(dist = n) %>%
  left_join(test_weekly_df, by = "date_admitted")

chunks_forecast_perf(
  pre_perf_df, "MLR + linear trend",
  scoringRules::crps_norm, mean(dist), sqrt(variance(dist))
)

forecast_plot_default(
  trend_fit, test_weekly_df,
  "Multiple linear regression + linear trend", FALSE
)
```

## Nonlinear trend
```{r}
nonlinear_trend_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  TSLM, as.formula(
    sprintf(
      "n ~ %s + trend(knots = c(2016))",
      paste(covar_names, collapse = " + ")
    )
  )
)

pre_perf_df <- nonlinear_trend_fit %>%
  select(date_admitted, n, .mean, startweek) %>%
  rename(dist = n) %>%
  left_join(test_weekly_df, by = "date_admitted")

chunks_forecast_perf(
  pre_perf_df, "MLR + nonlinear trend",
  scoringRules::crps_norm, mean(dist), sqrt(variance(dist))
)

forecast_plot_default(
  nonlinear_trend_fit, test_weekly_df,
  "Multiple linear regression + nonlinear trend", FALSE
)
```


## Seasonal dummy variable

```{r}
season_n_trend_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  TSLM, as.formula(sprintf("n ~ %s + trend() + season(period = 52)", paste(covar_names, collapse = " + ")))
)

pre_perf_df <- season_n_trend_fit %>%
  select(date_admitted, n, .mean, startweek) %>%
  rename(dist = n) %>%
  left_join(test_weekly_df, by = "date_admitted")

chunks_forecast_perf(
  pre_perf_df, "MLR + seasonal dummy + trend",
  scoringRules::crps_norm, mean(dist), sqrt(variance(dist))
)

forecast_plot_default(
  season_n_trend_fit, test_weekly_df, "Multiple linear regression + seasonal dummy + trend",
)
```

## Fourier series
Fourier terms `K` maximum is `m/2` where `m` is the seasonal period (52 for weekly data). When `K = m/2`, it functions similar to seasonal dummy variables, but has less predictors (52 vs 26).
```{r}
fourier_n_trend_fit <- forecast_chunks(
  train_weekly_weather_df, test_weekly_weather_df, seq(0, 49, 3),
  TSLM, as.formula(sprintf("n ~ %s + trend() + fourier(K = 26)", paste(covar_names, collapse = " + ")))
)

pre_perf_df <- fourier_n_trend_fit %>%
  select(date_admitted, n, .mean, startweek) %>%
  rename(dist = n) %>%
  left_join(test_weekly_df, by = "date_admitted")

chunks_forecast_perf(
  pre_perf_df, "MLR + fourier + trend",
  scoringRules::crps_norm, mean(dist), sqrt(variance(dist))
)

forecast_plot_default(
  fourier_n_trend_fit, test_weekly_df, "Multiple linear regression + fourier + trend",
)
```

# Generalized linear models

## Parallelization setup
```{r}
cl <- makeCluster(9)
invisible(clusterEvalQ(cl, library(magrittr)))
invisible(clusterEvalQ(cl, library(dplyr)))
invisible(clusterEvalQ(cl, library(purrr)))
invisible(clusterEvalQ(cl, library(tscount)))
invisible(clusterEvalQ(cl, library(distributional)))
invisible(clusterEvalQ(cl, library(tsibble)))
clusterExport(cl, c(
  "recur_miso", "train_weekly_weather_df", "test_weekly_weather_df",
  "test_weekly_df", "chunks_forecast_perf", "model_perfs", "boot_pi"
))
```


## With covariables

```{r}
glm_covar_fits <- function(distr) {
  parLapply(cl, covar_names, \(covar){
    fit <- recur_miso(
      train_weekly_weather_df, test_weekly_weather_df, seq(1, 49, 3),
      xreg_names = c(covar), link = "log", distr = distr
    ) %>%
      mutate(
        date_admitted = yearweek(paste0("2019 W", actualweek)),
        .before = everything()
      ) %>%
      rename(.mean = preds, n = dist)

    pre_perf_df <- fit %>%
      select(date_admitted, n, .mean, startweek) %>%
      rename(dist = n) %>%
      left_join(test_weekly_df, by = "date_admitted")

    chunks_forecast_res_df <- chunks_forecast_perf(
      pre_perf_df, sprintf("Poisson + %s", covar),
      scoringRules::crps_norm, mean(dist), sqrt(variance(dist))
    )

    tibble(
      model = sprintf("Poisson + %s", covar),
      RMSE = mean(chunks_forecast_res_df$RMSE),
      CRPS = mean(chunks_forecast_res_df$CRPS),
      covar = covar
    )
  }) %>% list_c()
}

poi_covar_fits <- glm_covar_fits("poisson")
nb_covar_fits <- glm_covar_fits("nbinom")
```

```{r}
poi_covar_fits %>% ggplot() +
  geom_col(aes(x = CRPS, y = fct_reorder(model, desc(CRPS))))
```

```{r}
nb_covar_fits %>% ggplot() +
  geom_col(aes(x = CRPS, y = fct_reorder(model, desc(CRPS))))
```


## Covariable selection

```{r}
full_model_glm <- glm(
  as.formula(paste0("n ~ ", paste(covar_names, collapse = " + "))),
  family = "poisson",
  data = train_weekly_weather_df %>%
    as_tibble() %>%
    select(-date_admitted)
)
stepwise_forward <- glmtoolbox::stepCriterion(
  full_model_glm,
  criterion = "adjr2",
  direction = "forward", trace = FALSE
)
stepwise_backward <- glmtoolbox::stepCriterion(
  full_model_glm,
  criterion = "adjr2",
  direction = "backward", trace = FALSE
)

stepwise_forward$final
stepwise_backward$final
```


```{r}
clusterExport(cl, c("stepwise_forward", "stepwise_backward", "as_tibble_col"))

fsel_covar_glm <- recur_miso_glm(
  train_weekly_weather_df, test_weekly_weather_df, seq(1, 49, 3),
  glm_formula = as.formula(paste0("n ", stepwise_forward$final)),
  cl = cl
) %>%
  mutate(
    date_admitted = yearweek(paste0("2019 W", actualweek)),
    .before = everything()
  )

bsel_covar_glm <- recur_miso_glm(
  train_weekly_weather_df, test_weekly_weather_df, seq(1, 49, 3),
  glm_formula = as.formula(paste0("n ", stepwise_forward$final)),
  cl = cl
) %>%
  mutate(
    date_admitted = yearweek(paste0("2019 W", actualweek)),
    .before = everything()
  )
```

```{r}
p1_fsel <- forecast_plot_default(
  fsel_covar_glm %>% rename(.mean = preds),
  test_weekly_df, "",
  funnel = FALSE
)
p1_fsel

p1_bsel <- forecast_plot_default(
  bsel_covar_glm %>% rename(.mean = preds),
  test_weekly_df, "",
  funnel = FALSE
)
p1_bsel
```


```{r}
fsel_pre_perf_df <- fsel_covar_glm %>%
  select(date_admitted, preds, dist, startweek) %>%
  rename(.mean = preds) %>%
  left_join(test_weekly_df, by = "date_admitted")

chunks_forecast_res_df <- chunks_forecast_perf(
  fsel_pre_perf_df, "Poisson",
  scoringRules::crps_sample, matrix(parameters(dist)$x[[1]], nrow = n())
)

p2_fsel <- metrics_plot(chunks_forecast_res_df, fsel_pre_perf_df$date_admitted)
p1_fsel / p2_fsel


bsel_pre_perf_df <- bsel_covar_glm %>%
  select(date_admitted, preds, dist, startweek) %>%
  rename(.mean = preds) %>%
  left_join(test_weekly_df, by = "date_admitted")

chunks_forecast_res_df <- chunks_forecast_perf(
  bsel_pre_perf_df, "Poisson",
  scoringRules::crps_sample, matrix(parameters(dist)$x[[1]], nrow = n())
)

p2_bsel <- metrics_plot(chunks_forecast_res_df, bsel_pre_perf_df$date_admitted)
p1_bsel / p2_bsel
```

# Parallelization teardown
```{r}
stopCluster(cl)
```


# Comparison

```{r}
model_perfs
```

```{r}
model_perfs %>% write_csv("regression_models_perf.csv")
```
