---
output: html_document
---

# Libraries

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(tscount)

library(parallel)
```

# Settings
```{r}
theme_set(theme_bw())
```


# Data ingestion

```{r}
source("../time_series_modelling/data_weekly.R")
```

# Framework
Goal: forecast 4 weeks at a time, with different starting points within a year
How:
  - Recursive multi-step forecasting (recursive MISO), predicts week-1 using the past 4 observed values, use that prediction + past 3 observed values as the new input to predict week-2, repeat for week-3 and week-4
  - Direct multistep forecasting (direct MISO), predicts week-1, week-2, ..., week-4 independently, using the 4 different models, one trained to predict 1 week ahead, one trained to predict 2 weeks ahead, etc.

## Recursive MISO - recursive multi-step forecasting

### Functions

```{r}
recur_miso <- function(train_set, test_set, cl = NULL) {
  if (!missing(cl)) {
    clusterEvalQ(cl, suppressPackageStartupMessages(library(magrittr)))
    clusterEvalQ(cl, suppressPackageStartupMessages(library(dplyr)))
    clusterEvalQ(cl, library(tscount))
    clusterExport(cl, c("train_set", "test_set"), environment())
  }

  pbapply::pblapply(seq(1, 49, 3), \(start_idx) {
    train_df <- train_set %>%
      bind_rows(test_set %>% slice_head(n = start_idx)) %>%
      tail(nrow(train_set))

    fit <- tsglm(train_df$n, model = list(past_obs = 1:4), link = "log", distr = "poisson")
    pred <- predict(fit, 4, newobs = NULL)

    tibble(
      startweek = start_idx,
      actualweek = start_idx + 0:3,
      preds = pred$pred,
      lowers = pred$interval[, "lower"],
      uppers = pred$interval[, "upper"],
    )
  }, cl = cl) %>% list_c()
}


forecast_layer <- function(frcst_df) {
  # frcst_df <- forecast_df
  frcst_df %<>% group_by(startweek) %>% group_split()

  layers <- lapply(
    frcst_df,
    \(df)
    c(layer(
      data = df,
      geom = "ribbon", stat = "identity", position = "identity",
      mapping = aes(x = date, ymin = lowers, ymax = uppers),
      params = list(alpha = 0.5, fill = "pink")
    ), layer(
      data = df,
      geom = "line", stat = "identity", position = "identity",
      mapping = aes(x = date, y = preds), params = list(color = "red")
    ))
  )
}
```

### Forecast
```{r}
cl <- makeCluster(4)
pred_results <- recur_miso(train_weekly_df, val_weekly_df, cl = cl)
stopCluster(cl)

recur_miso_forecast_df <- pred_results %>%
  mutate(date = yearweek(paste0("2018 W", actualweek)), .before = everything())


ggplot(val_weekly_df) +
  geom_line(aes(x = date_admitted, y = n)) +
  forecast_layer(recur_miso_forecast_df) +
  scale_x_yearweek(
    breaks = as.Date(val_weekly_df$date_admitted[seq(1, 52, 3)]),
    date_labels = "W%W",
    minor_breaks = NULL
  )
```

### Performance

```{r}
rmse <- sqrt(mean((forecast_df$preds - val_weekly_df$n)^2))
rmse
```

## Direct MISO - direct multistep forecasting
### Functions
```{r}
direct_miso <- function(train_set, test_set, cl = NULL) {
  if (!missing(cl)) {
    clusterEvalQ(cl, suppressPackageStartupMessages(library(magrittr)))
    clusterEvalQ(cl, suppressPackageStartupMessages(library(dplyr)))
    clusterEvalQ(cl, library(tscount))
    clusterExport(cl, c("train_set", "test_set"), environment())
  }

  pbapply::pblapply(seq(1, 49, 3), \(start_idx) {
    train_df <- train_set %>%
      bind_rows(test_set %>% slice_head(n = start_idx)) %>%
      tail(nrow(train_set))

    four_step_res <- lapply(0:3, \(i) {
      model <- list(past_obs = i + 1:4)
      fit <- tsglm(train_df$n, model)
      pred <- predict(fit, i + 1)

      tibble(
        startweek = start_idx,
        actualweek = start_idx + i,
        preds = pred$pred %>% tail(1),
        lowers = pred$interval[, "lower"] %>% tail(1),
        uppers = pred$interval[, "upper"] %>% tail(1)
      )
    })

    four_step_res %>% list_c()
  }) %>%
    list_c()
}
```

### Forecast
```{r}
cl <- makeCluster(4)
pred_results <- direct_miso(train_weekly_df, val_weekly_df, cl = cl)
stopCluster(cl)

direct_miso_forecast_df <- pred_results %>%
  mutate(date = yearweek(paste0("2018 W", actualweek)), .before = everything())

ggplot(val_weekly_df) +
  geom_line(aes(x = date_admitted, y = n)) +
  forecast_layer(direct_miso_forecast_df) +
  scale_x_yearweek(
    breaks = as.Date(val_weekly_df$date_admitted[seq(1, 49, 3)]),
    date_labels = "W%W",
    minor_breaks = NULL
  )
```

### Performance

```{r}
rmse <- sqrt(mean((direct_miso_forecast_df$preds - val_weekly_df$n)^2))
rmse
```
